Exploratory analysis of context: Regression Analysis

### 2022-11-07 analysis/exploratory/context_versus_nocontext/rscripts/analysis.Rmd
Task model with Wh predictor

View(d.ms.ma)
contrasts(d.ms.ma$Wh)
```

@@

>>>>

# View(d.ms.ma)
contrasts(d.ms.ma$Wh)
```

@@

# Is there an interaction between Paraphrase, Task AND WH?
##

# m.ms.ma.full.Wh = lmer(normed_rating ~ Wh*cTask + (1+Wh|workerid) + (1+Wh+cTask|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full.Wh, "../models/model-task-wh.rds")

m.ms.ma.full.Wh <- readRDS("../models/model-task-wh.rds")
summary(m.ms.ma.full.Wh)

## and paraphrase?
```{r}

# m.ms.ma.full.Wh.three = lmer(normed_rating ~ Wh*cParaphrase*cTask + (1+Wh+cParaphrase|workerid) + (1+Wh+cParaphrase+cTask|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full.Wh.three, "../models/model-task-para-wh.rds")

m.ms.ma.full.Wh.three <- readRDS("../models/model-task-para.rds")
summary(m.ms.ma.full.Wh.three)
